\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-29 paper.tex
Minor changes. With mmerge. Again

\author{
         Ben Upenieks, Chaitanya Varier,\\
         Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
         Nicholas Geofroy, Tony Meng, Vincent-Olivier Roch\\
         University of Waterloo\\
         \\
         \tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
         \\ \tt\small cdkphan@uwaterloo.ca, jdrwilli@uwaterloo.ca,
         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca
}

@@

The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
We use this data, in combination with the manually annotated data in order to create the collision dataset.
This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
As part of this data, we identify participants and bystanders, both known as agents. Participants are objects that are involved in a collision identified in the metadata, while bystanders are objects that are not.

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}" contains a description of the video as scraped from the video hosting website
  \item "\texttt{state}" is a string that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}" contains the site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}" is an object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}" is a string that represents the type of the video
  \item "\texttt{url}" is the url that the video was fetched from
  \item "\texttt{is\_split\_url}" is a boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}" is a list of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}" is the start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}" is the end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}" contains all bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}" is a list of frame numbers indicating the collision start frames
    \item "\texttt{resolution}" is a list with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}" is a list of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}" is a  unique numerical identifier that represents this object
      \item "\texttt{bboxes}" is a list of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}" represents the class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}" is a boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

>>>>

\author{
         Ben Upenieks, Chaitanya Varier,\\
         Curtis Duy Kha Phan, Jack David Roberts Williamson,\\
         Nicholas Geofroy, Chengzhong Meng, Vincent-Olivier Roch\\
         University of Waterloo\\
         \\
         \tt\small ben.upenieks@uwaterloo.ca, cvarier@uwaterloo.ca,
         \\ \tt\small cdkphan@uwaterloo.ca, jdrwilli@uwaterloo.ca,
         \\ \tt\small nicholas.geofroy@uwaterloo.ca, c24meng@uwaterloo.ca, vroch@uwaterloo.ca
}

@@

The pipeline uses web-scraping techniques to fetch the video data from these websites, along with a set of video metadata, describing the video's contents.
We use this data, in combination with the manually annotated data in order to create the collision dataset.
This combination allows us to take advantage of the wide variety of videos available on the internet, while still having reliable data that has been curated manually.
As part of this data, we identify participants and bystanders, both known as agents. Participants are objects that are involved in a collision identified in the metadata, while bystanders are uninvolved objects.

@@

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site specific
  \item "\texttt{title}": String that represents the type of the video
  \item "\texttt{url}": Url that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if all of the frames of the video are covered in this metadata item and false if no
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video that the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{end\_i}": The end frame of the video the bounding boxes are created for (if is\_split\_url is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (Width,Height) representing the resolution of the video the bounding boxes were created for in number of pixels 
    \item "\texttt{objects}": List of all of the bounding boxes for each object in the video. An object being either a vehicle or pedestrian. Within each object, there is metadata specific to that object.
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a 1x5 array with elements (frame number, x1, y1, x2, y2)
      \item "\texttt{class}": The class of the object, such as "car", "pedestrian"
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}
